---
title: "Homework 2"
author: "Matthew Borelli & Isaac Hulsey"
date: "2/2/2020"
output: md_document
---

```{r data, include=FALSE}
library(readr)
library(ggplot2)
library(dplyr)
library(plyr)
library(knitr)
library(stargazer)
brca = read.csv("D:/Documents/MA_Econ/Spring/ECO395M/My Work/Homework/ECO395M_HW2/data/brca.csv")
online_news = read.csv("D:/Documents/MA_Econ/Spring/ECO395M/My Work/Homework/ECO395M_HW2/data/online_news.csv")
```

# A Hospital Audit

## Introduction

The main goal of this statistical analysis is to audit the performance of your radiologists for mammogram screenings. Each doctor wants to limit the amount of false positives and false negatives as much as possible, but mammograms are not perfect. Therefore, it is reasonable to not expect 100% accuracy from your radiologists. However, we can utilize statistical analyses in order to see how efficient the radiologists are at recalling patients. Using the data you provided, approximately 1000 mammogram screenings from five randomly selected radiologists, we want to examing two important questions for you:

- Are some radiologists more clinically conservative than others in recalling patients, holding patient risk factors equal?
- When the radiologists at this hospital interpret a mammogram to make a decision on whether to recall the patient, does the data suggest that they should be weighing some clinical risk factors more heavily than they currently are?

## Conservative Radiologists

The naive method for analyzing conservativeness amongst your radiologists would be to look at the raw recall rates. Radiologists with a lower than average recall rate would be considered "conservative". Below is a bar chart showing the raw recall rates for each of the radiologists in our sample.

```{r initial, echo=FALSE}
conserv = as.data.frame(xtabs(~ radiologist + recall, brca))

radio_conserv = data.frame(Radiologist=levels(conserv$radiologist),
                           stringsAsFactors = FALSE)

for (i in 1:5) {
  no_recall_raw = conserv[1, 3]
  recall_raw = conserv[i + 5, 3]
  radio_conserv[i, 2] = (recall_raw)/(no_recall_raw + recall_raw)
}
colnames(radio_conserv)[2] <- "Recall_PCT"

ggplot(data = radio_conserv, mapping = aes(x = Radiologist, y = Recall_PCT)) +
  geom_col(position = "stack") +
  labs(x = "")

```

Judging from this chart, we would say that radiologist 34 is more conservative in recalling patients than the other radiologists. However, this simple analysis overlooks an important nuance: Doctors might see different patients in systematic ways that affect their recall rates. The next step we took was to control for patient factors to see if any radiologists are  more conservative than others, holding all else fixed. The following is the results from a logit regression model with controls for breat cancer symptoms and breast density classification. All other controls in the data set given had no statistically significant effect on the probability of a recall. 

```{r recall_regress, echo=FALSE}
recall = glm(recall ~ radiologist + age + history + symptoms + menopause + density, data=brca, family=binomial)

# Of the controls, only symptoms and density had significant effects on recall, adjust model

recall_v2 = glm(recall ~ radiologist + symptoms + density, data=brca, family=binomial)
stargazer(recall_v2, type="text")
```

The logit regression results do not show significant coefficients for any of the radiologists. To note, radiologist 13 is the omitted radiologist. We see no signficanct difference for any of the other radiologists other than radiologist 85, who has a positive (less conservative) difference at the 10% level. It is possible that radiologists 34 and 85 are significantly different, but we can't really be certain that radiologist 34 is more conservative than the others. Overall, since we see that there aren't any radiologists in our sample that are significantally more conservative in recalling patients after using a logit model to hold risk factors constant.

## Importance of Clinical Risk Factors

Now, instead of analyzing what might affect the probability of a radiologist recalling a patient, we want to see what factors best predict the likelihood of a patient having breast cancer. To do this, we will use a few different classification methods in order to better understand what risk factors best predict the probability of breast cancer.

### Null Models

To start, we want to set a baseline that we can compare following models to. For our baseline, we use a null model which simply predicts the most likely answer for each observation.

```{r null, echo = FALSE}
table(Cancer = brca$cancer)
```

The null model, in this case predicting that each patient does not have cancer, has approximately a `r round(950/(950+37)*100, digits=2)`% accuracy rate, or equivalently a `round(100 - (950/(950+37)*100), digits=2)`% error rate. These statistics will be one part of our benchmark levels for evaluating the performance of the classificaiton models we will use.

We also want to look at the current performance of radiologists at your hospital, to see if the following statistical models would result in an improvement in recall accuracy.

```{r baseline, echo = FALSE}
baseline = table(Cancer = brca$cancer, Recall = brca$recall)
baseline
n = nrow(brca)
```

From this table, we can generate important medical statistics that will help us compare predictions from our model against the actual decisions of radiologists:

- Accuracy = `round(100*(sum(diag(baseline)/n)), digits = 2)`%
- Sensitivity = `round(100*baseline[2,2] / (sum(baseline[2,])), digits=2)`%
- Specificity = `round(100*(1 - (baseline[1,2] / sum(baseline[1,]))), digits = 2)`%
- Positive Predictive Value = `round(100*(1 - (baseline[1, 2] / sum(baseline[, 2]))), digits = 2)`

All of these give important information about the recall process, therefore we will analyze all of them for each model. However, the most important your case is the sensitivity, as the consequences of missing a case of breast cancer are worse than incorrectly suspecting that someone does have breast cancer. We will look at all four of these values, but focus on the sensitivity of these models in order to limit the possibility of missing breast cancer patients.


### Graphical Analysis

Before deciding on a model, we want to graphically look at the relationships between the risk factors and breast cancer diagnoses. To do this, we will graph simple two-way scatter plots for the risk factors in question.

- Age Category
```{r age_bar, echo = FALSE}
age_cancer_setup = as.data.frame(table(Age = brca$age,  Cancer = brca$cancer))
age_cancer = data.frame(Age=levels(age_cancer_setup$age),
                           stringsAsFactors = FALSE)
for (i in 1:4) {
  age_cancer[i, 1] = age_cancer_setup[i, 1]
  no_cancer = age_cancer_setup[i, 3]
  cancer = age_cancer_setup[i + 4, 3]
  age_cancer[i, 2] = cancer/(no_cancer + cancer)
}
age_cancer
p0 = ggplot(data = age_cancer)
p0 + geom_bar(stat = "identity", aes(x = V1, y = V2)) + 
     labs(x = "Age Category", y = "Pct. Diagnosed w/ Breast Cancer")
```

- History of Breast Biopsy/Surgery 
```{r history_bar, echo = FALSE}
history_cancer_setup = as.data.frame(table(History = brca$history,  Cancer = brca$cancer))
history_cancer = data.frame(History=levels(history_cancer_setup$age),
                           stringsAsFactors = FALSE)
history_cancer_setup
for (i in 1:2) {
  history_cancer[i, 1] = history_cancer_setup[i, 1]
  no_cancer = history_cancer_setup[i, 3]
  cancer = history_cancer_setup[i + 2, 3]
  history_cancer[i, 2] = cancer/(no_cancer + cancer)
}
history_cancer
p0 = ggplot(data = history_cancer)
p0 + geom_bar(stat = "identity", aes(x = V1, y = V2)) + 
     labs(x = "History of Breast Biopsy/Surgery", y = "Pct. Diagnosed w/ Breast Cancer")
```

-

```{r symptoms_bar, echo = FALSE}
symptoms_cancer_setup = as.data.frame(table(Symptoms = brca$symptoms,  Cancer = brca$cancer))
age_cancer = data.frame(Age=levels(age_cancer_setup$age),
                           stringsAsFactors = FALSE)
for (i in 1:4) {
  age_cancer[i, 1] = age_cancer_setup[i, 1]
  no_cancer = age_cancer_setup[i, 3]
  cancer = age_cancer_setup[i + 4, 3]
  age_cancer[i, 2] = cancer/(no_cancer + cancer)
}
age_cancer
p0 = ggplot(data = age_cancer)
p0 + geom_bar(stat = "identity", aes(x = V1, y = V2)) + 
     labs(x = "Age Category", y = "Pct. Diagnosed w/ Breast Cancer")
```

###

# Predicting When Articles Go Viral

## Introduction


